---
title: "jenga: a vignette"
output: rmarkdown::html_vignette
vignette: >
  \usepackage[utf8]{inputenc}
  %\VignetteIndexEntry{jenga: a vignette}
  %\VignetteEngine{knitr::rmarkdown}
---


# Help workflow with a jenga stack

Great, you've decided to look into jenga! Although we won't be playing a game, we can still have fun by making RData files a little easier to work with. Here is a typical example in which you may want to use a jenga stack.

## 1) Setting up a jenga stack

```{r}
library(jenga)
methods <- c("Method 1", "Method 2", "Method 3")
sims.1 <- create_stack(methods)
```


## 2) Looking at the status of your jenga stack

```{r}
status_stack(sims.1)
```


We can see that all slots are empty! Lets add some data to the slot. The default is to *save* the jenga stack to an RData file with the name of the stack. If you don't want to save it, but rather only commit to memory, set `save=FALSE`.

## 3) Updating your jenga stack

```{r}
res <-  c(1,2,3,4,5,6)

update_stack(stack=sims.1, objects = res, slots = "Method 1", save=FALSE)
```

We can now check on the status of our jenga stack again:

```{r}
status_stack(sims.1)
```

We can also update more than one slot at a time. Suppose we now have data for Methods 2 and 3. We can combine the results into a list and update 2 slots at once.

```{r}
res2 <- c(2,3,4,5,6,7)
res3 <- c(3,4,5,6,7,8)

res <- list(res2,res3)

update_stack(stack=sims.1, objects = res, slots =c("Method 2", "Method 3"), save=FALSE)
```

If we check the status of the stack again, we will see now that it is all filled!

```{r}
status_stack(sims.1)
```

## 4) Extending your jenga stack

Say now that you want to extend the stack to hold a fourth method for your simulation study. We can easily add another slot using the `extend_stack` function.

```{r}
new.method <- "Method 4"
extend_stack(stack=sims.1, new.slot = new.method )

status_stack(sims.1)
```


## 5) Merging jenga stacks (under development)

If you want to merge jenga stacks, then we can use the `merge_stack` function to make this easy.

```{r, echo=FALSE}
sims.2 <- lapply(sims.1, function(x) x[1:3])
sims.2 <- sims.2[1:2]
names(sims.2) <- c("Method 2-1", "Method 2-2")
```

```{r}
new.stack <- merge_stack(sims.1, sims.2)
```


